---
title: "RinAction-ArimaModel"
author: "RobinYao"
date: "2019.11.8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 序列的变换以及稳定性评估
first we see the time series data, and find it has trend, so We do a first-order difference, then through the adf test, we find the time series to be the stable.
```{r}
library(forecast)
library(tseries)
plot(Nile)
ndiffs(Nile)
dNile <- diff(Nile)
plot(dNile)
adf.test(dNile)
```
# Model Selection
show the acf and pacf of time series, to do the model selection
```{r}
Acf(dNile)
Pacf(dNile)
```
# Fit the Model
we choose the amima(0 , 1 , 1), then use the data to fit the model
```{r}
library(forecast)
fit <- arima(Nile , order = c(0 , 1 , 1))
fit
accuracy(fit)
```
# 模型评价
```{r}
qqnorm(fit$residuals)
qqline(fit$residuals)
Box.test(fit$residuals , type = "Ljung-Box")
```
# 预测
我们用前面得到的模型做预测，深灰色的是95%置信区间,浅灰色的是80%置信区间
```{r}
result <- forecast(fit , 3)
plot(result , xlab = "Year" , ylab = "Annual Flow")
```
# 自动识别Arima Model
除了上述那种人工的方法,还可以用程序来自动识别Arima模型,代码如下所示：
```{r}
library(forecast)
fit <- auto.arima(sunspots)
fit
forecast(fit , 3)
accuracy(fit)
```

